\clearemptydoublepage
\phantomsection
\addcontentsline{toc}{chapter}{Acknowledgements}	


%\chapter*{Acknowledgements}

\vspace*{2cm}

\begin{center}
{\Large \bf Acknowledgments}
\end{center}

\vspace{1cm}

There is not enough space on this page to name all the individuals that have
positively influenced this work. 
% Here, however I would like to include in one or another way all of  those that offered their support and through the duration of my studies.
First, I would like to thank all the support from my family in
Colombia and Spain. Their support and enormous understanding have been
extremely important. This culminating work is possible because of them. 

I would like to thank  the founders of  Gini GmbH for giving me the opportunity of working on such interesting topic.  I would like to thank  Dr. Christoph Ringlstetter who served as
my main advisor for this work, and with whom I had the chance to have
interesting conversation full of relevant feedback and important criticism. 
Special gratitude to my colleagues  Daniel and Agnes for investing a lot of their time and energy  proofreading and offering insightful comments and valuable feedback.

In the local side,  special thanks to  Dipl.Inf. Christian
Osendorfer for his great support and steering that helped me to set the right
scope for this work. 

Finally, I would like to thank all those that in one or another way supported me through the duration of the studies. Fellow students and friends I learned a lot from. All of them coming from different countries, but all sharing the same desire of becoming better persons everyday.  Thank you guys, you know who you are. 

%\hspace{10cm}

%\vspace{20mm}
\vspace*{0.35\textheight}

	\noindent
\hspace*{0.6\textwidth} Miguel Fernando Cabrera G. \\
\hspace*{0.6\textwidth} Munich, \today


%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End: 
